Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
PCC Workshop update

@@

@@

@@

\section{Biographies}

>>>>

The data collected by patients' devices has the potential to create a large volume of data, and therefore particular
consideration should be paid about who and where the data will be stored. In particular, it is likely
that existing providers of storage for electronic health records will not want to be burdened with the
administration costs of storing additional data. The longevity of third-party storage providers is
also a concern, because there has been a history of short-notice closures of EHR providers (such as Google Health).

@@

Particular care should be taken when deciding on a format to store the activity diaries. Ideally
a format will be machine-readable, using open standards (for example XML, RDF or JSON) and
following existing schematic/ontological knowledge modelling conventions. There are a 
number of medical ontologies that already exist, as well as vocabularies and systems (such as
SNOMED\cite{} and IDC-10) that focus on the medical domain. The hope is that by using
such systems, that the data collected by patients can be analysed more rapidly by clinical systems
and staff.

@@

One of the major concerns with storage of patient data is privacy. Indeed, there is also potentially
legal requirements on storing personal health data, depending on the nature of the data being
stored.

@@

\section{Biographies}
?
